refnx -- Neutron and X-ray reflectometry analysis in Python

### 2018-08-13 paper/manuscript.tex
spell check

The \Structure\ object represents the interfacial model, assembled from individual \Component\ objects in series. Each \Component\ represents a subset of the interface and selected attributes of the \Component\ can be described by physically relevant \Parameter\ objects. The simplest and most familiar \Component\ is a \Slab, which has a uniform scattering length density (SLD), thickness, roughness, and volume fraction of solvent. The simplest models are simply a series of \Slab\ objects.
More sophisticated components include \LipidLeaflet\ (a lipid monolayer, or one-half of a lipid bilayer) and \Spline\ (for freeform modelling of an SLD profile using spline interpolation).
It is straightforward to develop/modify new components for different structural functionality, a consequence of the program design.

@@

The \ptemcee\ package is a variant (a `fork' in open-source software development terms) of the \emcee\ package that has been extended to implement the parallel tempering algorithm for characterisation of multi-modal probability distributions; different modes can be traversed by chain populations at higher `temperatures', while individual modes are efficiently explored by chains at lower `temperatures' \cite{ptemcee}.  Having multiple populations in the parallel tempering algorithm allows the sampler to escape local maxima, greatly aiding it's ability to explore the most probable regions of the posterior.  \ptemcee\ is also able to estimate the log-evidence term (the denominator in Equation~\ref{eqn:2}), which is useful when calculating the Bayes factor for model comparison.
%FIXME: reference for model selection...

>>>>

The \Structure\ object represents the interfacial model, assembled from individual \Component\ objects in series. Each \Component\ represents a subset of the interface and selected attributes of the \Component\ can be described by physically relevant \Parameter\ objects. The simplest and most familiar \Component\ is a \Slab, which has a uniform scattering length density (SLD), thickness, roughness, and volume fraction of solvent. The simplest models are simply a series of \Slab\ objects.
More sophisticated components include \LipidLeaflet\ (a lipid monolayer, or one-half of a lipid bilayer) and \Spline\ (for free-form modelling of an SLD profile using spline interpolation).
It is straightforward to develop/modify new components for different structural functionality, a consequence of the program design.

@@

The \ptemcee\ package is a variant (a `fork' in open-source software development terms) of the \emcee\ package that has been extended to implement the parallel tempering algorithm for characterisation of multi-modal probability distributions; different modes can be traversed by chain populations at higher `temperatures', while individual modes are efficiently explored by chains at lower `temperatures' \cite{ptemcee}.  Having multiple populations in the parallel tempering algorithm allows the sampler to escape local maxima, greatly aiding it's ability to explore the most probable regions of the posterior.  \ptemcee\ is also able to estimate the log-evidence term (the denominator in Equation~\ref{eqn:2}), which is useful when calculating the Bayes factor for model comparison.
